---
title: "ofpe_newC_corn_soy_rotation"
author: "Qianqian Du"
date: "2024-09-12"
output: html_document
---

# Objective:

+ Run APSIM simulations through R, the trials follow OFPE setting- each plot/point randomly receive different amount of N rates in each year. Assuming homogeneous plots within fields.

+ Run corn-soy rotation simulations 
  + corn, ofpe setting
  + soy 
    + consistent seeding rates
    + ofpe setting with seeding rates
    

# uplode the packages
```{r, message=FALSE, warning=FALSE}
# update the apsimx package as the latest version
# library(remotes)
# remotes::install_github('femiguez/apsimx')

library(apsimx)
library(tidyverse)
library(ggplot2)
library(data.table)
library(oce)
library(lubridate)

``` 

```{r}

### ============ set path to the file ============ ###
extd.dir = "/Users/qianqiandu/Library/CloudStorage/Box-Box/OFPE_heterogeneity_residue_N/Codes/Analysis/New_cultivar"

write_dir = "/Users/qianqiandu/Library/CloudStorage/Box-Box/OFPE_heterogeneity_residue_N/Codes/Analysis/New_cultivar"



###========== Check parameters of the file =========###
inspect_apsimx("ofpe_newC_soy_corn.apsimx", src.dir = extd.dir, node = "Clock")


edit_apsimx("ofpe_newC_soy_corn.apsimx", src.dir = extd.dir,
              wrt.dir = write_dir, node = "Clock",
              parm = "Start", value = "01/01/2015")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx", src.dir = extd.dir,
              wrt.dir = write_dir, node = "Clock",
              parm = "End", value = "01/01/2020", overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx", src.dir = extd.dir, node = "Clock")


inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx", src.dir = extd.dir, node = "Weather")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx", src.dir = extd.dir,
              wrt.dir = write_dir, node = "Weather",
              value = "fake_weather.met", overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx", src.dir = extd.dir, node = "Weather")

```

# Consistent trial designs 
The plots get more N always get more N.

```{r}

###=============================================================###
#####======== change the N rates in Operations through R =========#
###=============================================================###

#### Editing just one operation, need to change all three ####

simulation_result <- data.frame()

N_rates <- list(seq(0, 270, by = 30))

for (i in 1:length(N_rates[[1]])) {

N = as.character(N_rates[[1]][i])

new.date <- "2015-05-05"
# new.action <- '[Fertiliser].Apply(Amount: 0, Type: Fertiliser.Types.UAN_N, Depth: 30)'
new.action <- paste0("[Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")

# new.line <- '2015-05-05 [Fertiliser].Apply(Amount: 0, Type: Fertiliser.Types.UAN_N, Depth: 30)'
new_line <- paste0("2015-05-05 [Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Line'))


##--------------- change the 2nd year's N fertilizer amount -------------##
new.date <- "2017-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2017-05-05 [Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Line'))



##--------------- change the 3rd year's N fertilizer amount -------------##
new.date <- "2019-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2019-05-05 [Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Line'))


##--------------- change the 4th year's N fertilizer amount -------------##
new.date <- "2021-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2021-05-05 [Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(48, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(48, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(48, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(48, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(48, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(48, 'Line'))


##--------------- change the 5th year's N fertilizer amount -------------##
new.date <- "2023-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2023-05-05 [Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(63, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(63, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(63, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(63, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(63, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(63, 'Line'))



#######============== Run simulations =============#######
simulation <- apsimx("ofpe_newC_soy_corn-edited.apsimx", src.dir = write_dir, value = "Report") %>% 
  data.table()
  
#######============== Clean simulation results =============#######
  simulation_data <- simulation %>%  
  .[, applied_N := as.character(N)] %>% 
  setnames(c("Soil.Nutrient.MineralN(1)", "Soil.Nutrient.MineralN(2)", "Soil.Nutrient.MineralN(3)", "Soil.Nutrient.MineralN(4)", "Soil.Nutrient.MineralN(5)", "Soil.Nutrient.MineralN(6)", "Soil.Nutrient.MineralN(7)", "Soil.Nutrient.MineralN(8)"), c("Mineral_1", "Mineral_2", "Mineral_3","Mineral_4","Mineral_5","Mineral_6","Mineral_7", "Mineral_8")) %>% 
  .[, .(Date, applied_N, NO3, NO3Leaching, AnnualNleaching, AnnualSoilMineral, AnnualNfertilizer, TotalMineralization, SoilMineralization, CropYieldMaize, CropYieldSoy, Mineral_1, Mineral_2, Mineral_3, Mineral_4, Mineral_5, Mineral_6, Mineral_7, Mineral_8)] %>% 
  .[, year := as.numeric(format(simulation$Date, "%Y"))] %>%
  .[, month := as.numeric(format(simulation$Date, "%m"))] %>% 
  .[, day := as.numeric(format(simulation$Date, "%d"))]


###--- store the data ---###

simulation_result <- rbind(simulation_result, simulation_data)

}

# saveRDS(simulation_result, "/Users/qianqiandu/Desktop/N_Residual_APSIM/Git_Controled/consistent_rate_trials/same_weather_cons_N.rds")


```

## Look at the result
```{r}

yield_analysis <- simulation_result %>% 
  data.table() %>% 
  .[, .(yield_M = max(CropYieldMaize), yield_S = max(CropYieldSoy)), by = c("year", "applied_N")]


consistent_corn_response <- ggplot(data = yield_analysis[year != 2015 & yield_M != 0, ])+
  geom_point(aes(x = as.numeric(applied_N), y = yield_M, color = factor(year)))+
  geom_line(aes(x = as.numeric(applied_N), y = yield_M, color = factor(year)))+
  ylab("yield Maize")+
  ggtitle("corn yield response with consistent trial rates in CS rotation")+
  theme_bw()


consistent_soy_response <- ggplot(data = yield_analysis[year != 2015 & yield_S != 0, ])+
  geom_point(aes(x = year, y = yield_S, color = (applied_N)))+
  ylab("yield Soy")+
  ggtitle("Soy yield with consistent trial rates in CS rotation")+
  theme_bw()


  

ggplot(data = simulation_data)+
  geom_point(aes(x =Date , y = CropYieldMaize), color = "yellow")+
  geom_point(aes(x =Date , y = CropYieldSoy), color = "green")



```


# Run OFPE on N trials 
```{r}
N_rates <- data.frame(
    var_N = as.character(seq(0, 270, by = 30))
  )

run_simpulation <- function(iteration_id, N_rates){
  
  number_years <- 5
  
  N <- sample(N_rates$var_N, number_years, replace = TRUE)


new.date <- "2015-05-05"
# new.action <- '[Fertiliser].Apply(Amount: 0, Type: Fertiliser.Types.UAN_N, Depth: 30)'
new.action <- paste0("[Fertiliser].Apply(Amount: ",N[1],", Type: Fertiliser.Types.UAN_N, Depth: 30)")

# new.line <- '2015-05-05 [Fertiliser].Apply(Amount: 0, Type: Fertiliser.Types.UAN_N, Depth: 30)'
new_line <- paste0("2015-05-05 [Fertiliser].Apply(Amount: ",N[1],", Type: Fertiliser.Types.UAN_N, Depth: 30)")


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Line'))


##--------------- change the 2nd year's fertilizer amount -------------##
new.date <- "2017-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N[2],", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2017-05-05 [Fertiliser].Apply(Amount: ",N[2],", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Line'))




##--------------- change the 3rd year's fertilizer amount -------------##
new.date <- "2019-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N[3],", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2019-05-05 [Fertiliser].Apply(Amount: ",N[3],", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Line'))



##--------------- change the 4th year's fertilizer amount -------------##
new.date <- "2021-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N[4],", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2021-05-05 [Fertiliser].Apply(Amount: ",N[4],", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(48, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(48, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(48, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(48, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(48, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(48, 'Line'))


##--------------- change the 5th year's fertilizer amount -------------##
new.date <- "2023-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N[5],", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2023-05-05 [Fertiliser].Apply(Amount: ",N[5],", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(63, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(63, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(63, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(63, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(63, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(63, 'Line'))



#######============== Run simulations =============#######
simulation <- apsimx("ofpe_newC_soy_corn-edited.apsimx", src.dir = write_dir, value = "Report") %>% 
  data.table()
  
#######============== Clean simulation results =============#######
  simulation_data <- simulation %>%  
  # .[, applied_N := as.character(N)] %>%
  setnames(c("Soil.Nutrient.MineralN(1)", "Soil.Nutrient.MineralN(2)", "Soil.Nutrient.MineralN(3)", "Soil.Nutrient.MineralN(4)", "Soil.Nutrient.MineralN(5)", "Soil.Nutrient.MineralN(6)", "Soil.Nutrient.MineralN(7)", "Soil.Nutrient.MineralN(8)"), c("Mineral_1", "Mineral_2", "Mineral_3","Mineral_4","Mineral_5","Mineral_6","Mineral_7", "Mineral_8"), skip_absent = TRUE) %>% 
  .[, .(Date, NO3, NO3Leaching, AnnualNleaching, AnnualSoilMineral, AnnualNfertilizer, TotalMineralization, SoilMineralization, CropYieldMaize, CropYieldSoy, Mineral_1, Mineral_2, Mineral_3, Mineral_4, Mineral_5, Mineral_6, Mineral_7, Mineral_8)] %>% 
  .[, year := as.numeric(format(simulation$Date, "%Y"))] %>%
  .[, month := as.numeric(format(simulation$Date, "%m"))] %>% 
  .[, day := as.numeric(format(simulation$Date, "%d"))] %>% 
  .[, applied_N := sum(unique(AnnualNfertilizer)), by = year]

simulation_data$iteration_id <- iteration_id  # Add iteration ID to the result

return(simulation_data)

}


result_ofpe_trial <- lapply(1:80, function(x) run_simpulation(x, N_rates)) %>% 
  rbindlist()

# saveRDS(result_real_weather, file = "ofpe_real_weather.rds")

```


```{r}

view_ofpe_result <- result_ofpe_trial %>% 
  .[, .(yield_M = max(CropYieldMaize)), by = .(year, applied_N, iteration_id)]


ggplot(data = view_ofpe_result[year != 2015 & yield_M != 0, ])+
  geom_point(aes(x = applied_N, y = yield_M, color = factor(year)))+
  geom_smooth(aes(x = applied_N, y = yield_M, color = factor(year)))+
  ggtitle("OFPE yield response")+
  theme_bw()


```



# True yield response functions in each subplot 

# Simulations
```{r}
###---- create the dataset to store the result ----###
final_result <- data.frame()

###---- create N seq for trial designs ----###
N_rates <- data.frame(
    var_N = as.character(seq(0, 250, by = 5))
  )

number_plot <- 100

set.seed(230829)
###--- trial design ---###
applied_N <- data.frame(
  year_1 = sample(N_rates$var_N, number_plot, replace = TRUE),
  year_2 = sample(N_rates$var_N, number_plot, replace = TRUE),
  year_3 = sample(N_rates$var_N, number_plot, replace = TRUE),
  year_4 = sample(N_rates$var_N, number_plot, replace = TRUE),
  plot_id = seq(1, 100, by = 1)) %>% 
  as.list()


#################################################
###====== Loop for running simulations =======###
#################################################

# each loop iteration is one plot, 200 plots, so j = 1:200

# for (j in 1:length(applied_N_by_plots[[1]])) {
for (j in 21:50) {  
  
new.date <- "2015-05-05"
# new.action <- '[Fertiliser].Apply(Amount: 0, Type: Fertiliser.Types.UAN_N, Depth: 30)'
new.action <- paste0("[Fertiliser].Apply(Amount: ",applied_N[[1]][j],", Type: Fertiliser.Types.UAN_N, Depth: 30)")

# new.line <- '2015-05-05 [Fertiliser].Apply(Amount: 0, Type: Fertiliser.Types.UAN_N, Depth: 30)'
new_line <- paste0("2015-05-05 [Fertiliser].Apply(Amount: ",applied_N[[1]][j],", Type: Fertiliser.Types.UAN_N, Depth: 30)")


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Line'))

  # for (i in 1:nrow(N_rates)) {
##--------------- change the 2nd year's fertilizer amount -------------##
new.date <- "2017-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",applied_N[[2]][j],", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2017-05-05 [Fertiliser].Apply(Amount: ",applied_N[[2]][j],", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Line'))

  # inner loop is to get the true yield response function for each plot, i is the N rate applied for that plot.

  for (i in 1:nrow(N_rates)) {

#--------------- change the 3rd year's fertilizer amount -------------##
new.date <- "2019-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N_rates[[1]][i],", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2017-05-05 [Fertiliser].Apply(Amount: ",N_rates[[1]][i],", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Line'))


#######============== Run simulations =============#######
print(j)

simulation <- apsimx("ofpe_newC_soy_corn-edited.apsimx", src.dir = write_dir, value = "Report") %>% 
  data.table()
  

#######============== Clean simulation results =============#######
  simulation_data <- simulation %>%  
  .[, applied_N_i := N_rates[[1]][i]] %>%
  setnames(c("Soil.Nutrient.MineralN(1)", "Soil.Nutrient.MineralN(2)", "Soil.Nutrient.MineralN(3)", "Soil.Nutrient.MineralN(4)", "Soil.Nutrient.MineralN(5)", "Soil.Nutrient.MineralN(6)", "Soil.Nutrient.MineralN(7)", "Soil.Nutrient.MineralN(8)"), c("Mineral_1", "Mineral_2", "Mineral_3","Mineral_4","Mineral_5","Mineral_6","Mineral_7", "Mineral_8"), skip_absent = TRUE) %>% 
  .[, .(Date, NO3, NO3Leaching, AnnualNleaching, AnnualSoilMineral, AnnualNfertilizer, TotalMineralization, SoilMineralization, CropYieldMaize, CropYieldSoy, Mineral_1, Mineral_2, Mineral_3, Mineral_4, Mineral_5, Mineral_6, Mineral_7, Mineral_8)] %>% 
  .[, year := as.numeric(format(simulation$Date, "%Y"))] %>%
  .[, month := as.numeric(format(simulation$Date, "%m"))] %>% 
  .[, day := as.numeric(format(simulation$Date, "%d"))] %>% 
  .[, plot_id := as.character(j)] %>% 
  .[, applied_N := sum(unique(AnnualNfertilizer)), by = year]


final_result <- rbind(final_result, simulation_data)

  }

}

final_result$applied_N %>% unique()
final_result$plot_id %>% unique()
# saveRDS(final_result, "/Users/qianqiandu/Library/CloudStorage/Box-Box/OFPE_heterogeneity_residue_N/Data/Processed-Data/corn_soy_ofpe_B105.rds")


see_result <- final_result %>% 
  group_by(applied_N, plot_id) %>% 
  summarise(yield_max = max(CropYieldMaize))

ggplot(see_result)+
  geom_point(aes(x = applied_N, y = yield_max))

```


```{r}
## --- 2019 --- ##
simulation_true_yrp_2019 <-   readRDS("/Users/qianqiandu/Desktop/N_Residual_APSIM/Codes/corn_soy_rotation/corn_soy_rotation.rds") %>%
  rbind(readRDS("/Users/qianqiandu/Desktop/N_Residual_APSIM/Codes/corn_soy_rotation/corn_soy_rotation_2.rds")) %>%
  rbind(readRDS("/Users/qianqiandu/Desktop/N_Residual_APSIM/Codes/corn_soy_rotation/corn_soy_rotation_4.rds")) %>%
  rbind(final_result) %>% 
  data.table() %>% 
  .[year == 2019, ]

simulation_true_yrp_2019$applied_N <- as.character(simulation_true_yrp_2019$applied_N)
simulation_true_yrp_2019$plot_id <- as.character(simulation_true_yrp_2019$plot_id)

true_yrp_2019 <- simulation_true_yrp_2019 %>% 
  group_by(plot_id, applied_N) %>% 
  summarise(yield_max = max(CropYieldMaize)) %>% 
  data.table()



## --- 2019 --- ##

ofpe_2019 <- data.frame(
  applied_N = applied_N[[3]], 
  plot_id = applied_N[[5]]
)


ofpe_2019$plot_id <- as.character(ofpe_2019$plot_id)
ofpe_2019$applied_N <- as.character(ofpe_2019$applied_N)

ofpe_2019 <- left_join(ofpe_2019, true_yrp_2019, by = c("applied_N", "plot_id"))


simulation_true_yrp_2019$applied_N <- as.numeric(simulation_true_yrp_2019$applied_N)
ofpe_2019$applied_N <- as.numeric(ofpe_2019$applied_N)


ggplot()+
  geom_point(aes(x = as.numeric(applied_N), y = yield_max), data = true_yrp_2019, size = 0.3)+
  geom_line(aes(x = as.numeric(applied_N), y = yield_max, group = as.factor(plot_id)), data = true_yrp_2019, size = 0.3)+
  geom_point(aes(x = as.numeric(applied_N), y = yield_max), data = ofpe_2019, color = "blue")+
  geom_smooth(aes(x = as.numeric(applied_N), y = yield_max), data = ofpe_2019, size = 1.2)+
  ggtitle("true corn yield responses in each plot after 4 years corn-soy rotations")+
  ylab("yield")+
  theme_bw()+
  ylim(650, 850)


true_yrp_2019[applied_N == 0, ] %>% 
  .[, .(yield_max)] %>% 
  summary()


```


## Consistent trial design

```{r}

simulation_result <- data.frame()

N_rates <- list(seq(0, 270, by = 30))
N_rates_by5 <- list(seq(0, 240, by = 5))

for (j in 1:length(N_rates[[1]])) {

  j = 9
N = as.character(N_rates[[1]][j])

new.date <- "2015-05-05"
# new.action <- '[Fertiliser].Apply(Amount: 0, Type: Fertiliser.Types.UAN_N, Depth: 30)'
new.action <- paste0("[Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")

# new.line <- '2015-05-05 [Fertiliser].Apply(Amount: 0, Type: Fertiliser.Types.UAN_N, Depth: 30)'
new_line <- paste0("2015-05-05 [Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(3, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(3, 'Line'))

  # for (i in 1:nrow(N_rates)) {
##--------------- change the 2nd year's fertilizer amount -------------##
new.date <- "2017-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2017-05-05 [Fertiliser].Apply(Amount: ",N,", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(18, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(18, 'Line'))

  # inner loop is to get the true yield response function for each plot, i is the N rate applied for that plot.

  for (i in 1:length(N_rates_by5[[1]])) {
    
#--------------- change the 3rd year's fertilizer amount -------------##
new.date <- "2019-05-05"
new.action <- paste0("[Fertiliser].Apply(Amount: ",N_rates_by5[[1]][i],", Type: Fertiliser.Types.UAN_N, Depth: 30)")
new_line <- paste0("2019-05-05 [Fertiliser].Apply(Amount: ",N_rates_by5[[1]][i],", Type: Fertiliser.Types.UAN_N, Depth: 30)")

edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Date'),
            value = new.date,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Action'),
            value = new.action,
            overwrite = TRUE)


edit_apsimx("ofpe_newC_soy_corn-edited.apsimx",
            src.dir = write_dir,
            wrt.dir = write_dir,
            node = "Operations",
            parm = list(33, 'Line'),
            value = new.action,
            overwrite = TRUE)

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Date'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Action'))

inspect_apsimx("ofpe_newC_soy_corn-edited.apsimx",
               node = "Operations",
               parm = list(33, 'Line'))


#######============== Run simulations =============#######
print(j)

print(i)

simulation <- apsimx("ofpe_newC_soy_corn-edited.apsimx", src.dir = write_dir, value = "Report") %>% 
  data.table()
  

#######============== Clean simulation results =============#######
  simulation_data <- simulation %>%  
  .[, applied_N_i := N_rates[[1]][i]] %>%
  setnames(c("Soil.Nutrient.MineralN(1)", "Soil.Nutrient.MineralN(2)", "Soil.Nutrient.MineralN(3)", "Soil.Nutrient.MineralN(4)", "Soil.Nutrient.MineralN(5)", "Soil.Nutrient.MineralN(6)", "Soil.Nutrient.MineralN(7)", "Soil.Nutrient.MineralN(8)"), c("Mineral_1", "Mineral_2", "Mineral_3","Mineral_4","Mineral_5","Mineral_6","Mineral_7", "Mineral_8"), skip_absent = TRUE) %>% 
  .[, .(Date, NO3, NO3Leaching, AnnualNleaching, AnnualSoilMineral, AnnualNfertilizer, TotalMineralization, SoilMineralization, CropYieldMaize, CropYieldSoy, Mineral_1, Mineral_2, Mineral_3, Mineral_4, Mineral_5, Mineral_6, Mineral_7, Mineral_8)] %>% 
  .[, year := as.numeric(format(simulation$Date, "%Y"))] %>%
  .[, month := as.numeric(format(simulation$Date, "%m"))] %>% 
  .[, day := as.numeric(format(simulation$Date, "%d"))] %>% 
  .[, plot_id := as.character(j)] %>% 
  .[, applied_N := sum(unique(AnnualNfertilizer)), by = year]


simulation_result <- rbind(simulation_result, simulation_data)

  }

}

simulation_result$applied_N %>% unique()
simulation_result$plot_id %>% unique()
saveRDS(simulation_result, "/Users/qianqiandu/Library/CloudStorage/Box-Box/OFPE_heterogeneity_residue_N/Data/Processed-Data/corn_soy_consistent_B105.rds")



```

```{r}

consis_rate <- simulation_result %>% 
  .[year == 2019, ] %>% 
  group_by(plot_id, applied_N) %>% 
  summarise(yield_max = max(CropYieldMaize)) %>% 
  data.table()

ggplot(data = consis_rate)+
  geom_point(aes(x = applied_N, y = yield_max, color = plot_id))+
  geom_line(aes(x = applied_N, y = yield_max, color = plot_id))+
  theme_bw()
  # xlab("applied N")+
  # ylab("Corn yield")+
  # ylim(650, 850)

consis_rate[applied_N == 0, .(yield_max)] %>% 
  summary()

```



